---
title: "p8105_hw1_cl4043"
author: Stella Li
output: github_document
---


This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

as.numeric function tries to convert all objects into numeric values which do not work on character vectors, and will turn logical vectors into 0 and 1, and factor vectors into different numbers according to the level of factor.

```{r}
# convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# convert the logical vector to a factor, and multiply the random sample by the result
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2
```{r load data}
data("penguins", package = "palmerpenguins")
```

* There are `r ncol(penguins)` variables in this dataset, including `r names(penguins)`. Important values of variables include mean, range, and factor level, such as the mean of bill_length_mm is `r round(mean(penguins$bill_length_mm, na.rm = TRUE), digits=2)`, the range of bill_length_mm is `r range(penguins$bill_length_mm, na.rm = TRUE)`, and the factor level of sex is `r levels(penguins$sex)`, etc.

* The data set has `r ncol(penguins)` columns and `r nrow(penguins)` rows in total.

* The mean of the flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), digits=2)` mm.


```{r plot}
penguin_plot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point(aes(color = species))

penguin_plot
```

```{r saving the plot}
ggsave("penguin_plot.png", width = 5, height = 4)
```

